### 2016-08-12 Docs/managing_jobs/managingjobs.tex

>>>>

One very useful tool for determining target metrics and what is limiting your
performance is a spreadsheet developed by NVIDIA to calculate occupancy.  Every
installation of the CUDA Toolkit should have this occupancy calculator in a
tools subdirectory.  At time of writing, the calculator is also available at
this link:
\url{http://developer.download.nvidia.com/compute/cuda/CUDA_Occupancy_calculator.xls}.
The document is actually  more than a simple calculator.  It contains quite a
bit of interesting insight into optimizing a GPU code.  More on occupancy can be
found here:
\url{http://docs.nvidia.com/cuda/cuda-c-best-practices-guide/index.html#occupancy}.
